\section{Professional Employment}
\cventry{2016-present}{Assistant Professor}{Carnegie Mellon University}{Pittsburgh, PA}{}
  {Tenure-track position in the Computer Science Department with affiliate appointment in the Computational Biology Department.}
\cventry{2015-present}{Assistant Professor (Adjunct)}{Carnegie Mellon University}{Pittsburgh, PA}{}
  {Accepted and deferred tenure-track Assistant Professor position in the Computer Science Department, with an affiliate appointment in the Computational Bioiogy department.}
\cventry{2015-2016}{Postdoctoral Researcher}{Harvard Medical School}{Cambridge, MA}{}
  {Developing program verification and analysis techniques to aid in the construction of rule-based, graphical kinetic models for intracellular signalling.}
\cventry{Summer 2016}{Co-founder}{Cybersecurity Factory}{Cambridge, MA}{}
  {Started accelerator for early-stage cybersecurity companies with the goal of turning more research ideas into startups. Partnered with venture firm Highland Capital to run pilot program summer 2015.}
\cventry{2009-2015}{Research Assistant}{Massachusetts Institute of Technology}{Cambridge, MA}{}
  {Graduate research in programming languages.}
\cventry{Summer 2012}{Software Engineering Intern}{Facebook, Inc.}{Menlo Park, CA}{}{Built verifier for backend privacy language. Filed patent.}
\cventry{Summer 2010}{Research Intern, Programming Languages and Analysis Group}{Microsoft Research}{Redmond, WA}{}
  {Worked with Nikhil Swamy and Juan Chen on extending a security-typed language, to support secure marshalling and cryptographic proofs.}
\cventry{Summer 2009}{Research Intern, Operating Systems Group}{Microsoft Research}{Redmond, WA}{}
  {Worked with Chris Hawblitzel to build an operating system kernel verified for type-safety.}
\cventry{Summer 2008}{Software Engineering Intern}{Peerium, Inc.}{Cambridge, MA}
  {}{Worked at start-up creating a dependently typed functional language written in Haskell.  Created parser for core language; wrote compiler optimizations; worked on GUI libraries.}
\cventry{Summer 2007}{Software Engineering Intern}{Google, Inc.}{Santa Monica, CA}{}
  {Completed standalone project on video search team using C++.  Received full-time offer.}
\cventry{Summer 2006}{Research Intern}{Computational Biology Initiative, Harvard Medical School}{Boston, MA}{}
  {Worked with Dennis Wall and Leon Peshkin to develop and implement computational processes for tracing evolution and coevolution of presynaptic receptors.}
%%%
\cventry{Summer 2005}{Software Development Intern}{Mellon Financial}{Pittsburgh, PA}
  {}{Worked on data mapping and management project using SQL and ColdFusion.}
