\section{In the Media}
\subsection{Selected Press}
\cvline{MIT Tech Review}{``Why don't computers keep our personal data secure by default?'' Patrick Doyle, \emph{MIT Technology Review}, August 23, 2016.}{}
\cvline{TechCrunch}{``Coding In The Cloud Era Demands A Structural Rethink To Bake In Securirity And Privacy.'' Natasha Lomas, \emph{TechCrunch}, Sept. 27, 2015.}{}
\cvline{Wired}{``The Quest to Rescue Security Research from the Ivory Tower.'' Klint Finley, \emph{Wired}, July 2, 2015.}{}
\cvline{Fortune}{``Cybersecurity Factory Nurtures Early-Stage Startups in a Tough Field.'' Barb Darrow, \emph{Fortune}, June 26, 2015.}{}
\cvline{Boston Globe}{``MIT Students, Highland Capital, Partner to Launch Cybersecurity Factory.'' Janelle Nanos, \emph{The Boston Globe}, March 31, 2015.}{}
\cvline{Fast CoExist}{``A Better Way To Protect Privacy? Take The Programmer Out Of The Equation.'' Jessica Leber, \emph{Fast CoExist}, March 7, 2014.}{}
\cvline{Wired}{``Out in the Open: A New Programming Language With Built-In Privacy Protocols.'' Klint Finley, \emph{Wired}, March 3, 2014.}{}
\cvline{Gigaom}{``Want to build privacy into your apps? Check out Jeeves, now available in Python.'' Barb Darrow, \emph{Gigaom}, Feb. 11, 2014.}{}
\cvline{MIT Tech Review}{``New Programming Language Removes Human Error from Privacy Equation.'' MIT CSAIL, \emph{MIT Technology Review}, Feb. 10, 2014.}{}
\cvline{Gigaom}{``Cloud Trailblazers: 10 for 2013. Mission Possible? Jean Yang.'' Barb Darrow, \emph{Gigaom}, May 28, 2013.}
\cvline{New Scientist}{``What your online friends reveal about where you are.'' Jacob Aron, \emph{New Scientist}, January 25, 2012.}
%\cvline{}{\textbf{Softpedia} (2010): ``Verve - New non-Windows OS from Microsoft.'' Marius Oiaga, Dec. 10.}
%\cvline{}{\textbf{InfoQ} (2010): ``Announcing Verve - A Type-Safe Operating System.'' James Vastbinder, Dec. 8.}

\subsection{Book Appearances}
\cvline{}{Andi Deihn. \emph{Technology: Cool Women Who Code}. Nomad Press, 2015.}{}
