\section{Publications}
\subsection{Refereed Conference/Workshop Papers}
\cvline{PLDI 2016}{\textbf{Jean Yang}, Travis Hance, Thomas H. Austin, Armando Solar-Lezama, Cormac Flanagan, and Stephen Chong. Precise, Dynamic Information Flow for Database-Backed Applications. \emph{Programming Language Design and Implementation}.}{}
\cvline{JFP 2013}{Nikhil Swamy, Juan Chen, C\'{e}dric Fournet, Pierre-Yves Strub, Karthikeyan Bhargavan, and \textbf{Jean Yang}. Secure Distributed Programming with Value-Dependent Types. \emph{Journal of Functional Programming 23(4)}, July 2013.}{}
\cvline{PLAS 2013}{Thomas H. Austin, \textbf{Jean Yang}, Cormac Flanagan, and Armando Solar-Lezama. Faceted Execution of Policy-Agnostic Programs. \emph{Programming Languages and Security}, 2013.}{}
\cvline{POPL 2012}{\textbf{Jean Yang}, Kuat Yessenov, and Armando Solar-Lezama. A Language for Automatically Enforcing Privacy Policies. \emph{Principles of Programming Languages}, 2012.}{}
\cvline{CACM 2011}{\textbf{Jean Yang} and Chris Hawblitzel. Safe to the Last Instruction: Automated Verification of a Type-Safe Operating System. \emph{Communications of the Association for Computing Machinery}, December 2011.}
\cvline{ICFP 2011}{Nikhil Swamy, Juan Chen, C\'{e}dric Fournet, Pierre-Yves Strub, Karthikeyan Bharagavan, and \textbf{Jean Yang}. Secure Distributed Programming with Value-Dependent Types. \emph{International Conference on Functional Programming}, 2011.}{}
\cvline{PLDI 2010}{\textbf{Jean Yang} and Chris Hawblitzel. Safe to the Last Instruction: Automated Verification of a Type-Safe Operating System. \emph{Programming Language Design and Implementation}, 2010. \textbf{Best Paper Award.}}

\subsection{Technical Reports}
\cvline{2016}{Nadia Polikarpova, Jean Yang, Shachar Itzhaky, and Jean Yang. Type-Driven Repair for Information Flow Security. \url{https://arxiv.org/abs/1607.03445}}

\subsection{Patents Issued}
\cvline{2013}{Stephen C. Heise, \textbf{Jean Yang}, Dwayne Reeves, and Yiding Jia. Privacy verification tool. US20140282837 A1, filed March 15, 2013 and issued April 14, 2015.}{}
\cvline{2010}{Chris Hawblitzel and \textbf{Jean Yang}. Automated verification of a type-safe operating system. US8341602 B2, filed February 27, 2010 and issued December 25, 2012.}{}


