\section{Speaking}
\subsection{Invited Research Talks}
\cvline{2017}{``Preventing Information Leaks by Construction''}
\cvlistitem{Curry On Barcelona! (June 2017)}
\cvlistitem{Programming Languages Mentory Workshop, colocated with PLDI (June 2017)}
\cvlistitem{\'{E}cole Normale Sup\'{e}rieure (January 2017)}
\cvline{}{``Analyses for Rule-Based Models of Cellular Signalling'', Cambridge University (May 2017)}{}
\cvline{}{``Policy-Agnostic Programming for Preventing Information Leaks''}{}
\cvlistitem{INRIA Paris (June 2017)}
\cvlistitem{Oxford University (May 2017)}
\cvlistitem{The 2nd Summit on Advances in Programming Languages (May 2017)}
\cvline{}{``Policy-Agnostic Programming for Database-Backed Applications,'' Cornell University (April 2017)}{}
\cvline{}{``Preventing Information Leaks by Construction,'' \'{E}cole Normale Sup\'{e}rieure (January 2017)}{}
\cvline{2016}{``A Logical Deduction Tool for Assembly,'' 6th Workshop on Logic and Systems Biology (July 2016)}
\cvline{2015}{``Preventing Information Flow Leaks with Jeeves,'' Singapore Data Privacy Workshop (July 2015)}
\cvline{}{``Preventing Information Leaks with Jeeves''}
\cvlistitem{Columbia University (Special Seminar, February 2015)}
\cvlistitem{University of California, Berkeley (Special Seminar, March 2015)}
\cvlistitem{University of Illinois, Urbana-Champaign (Special Seminar, April 2015)}
\cvlistitem{Carnegie Mellon University (Special Seminar, April 2015)}
\cvlistitem{Microsoft Research Redmond (April 2015)}
\cvlistitem{Samsung Research (April 2015)}
\cvline{2011-2014}{``Jeeves: A Language for Automatically Enforcing Privacy Policies''}{}
\cvlistitem{Cornell University (August 2014)}
\cvlistitem{Columbia University (May 2014)}
\cvlistitem{Microsoft Research - Cambridge (October 2013)}
\cvlistitem{Gigaom Structure Conference (June 2013)}
\cvlistitem{Tufts University (Colloquium, December 2012)}
\cvlistitem{Brown University (June 2012)}
\cvlistitem{University of California, Berkeley (April 2012)}
\cvlistitem{Google - Mountain View (April 2012)}
\cvlistitem{Facebook - Menlo Park (March 2012)}
\cvlistitem{Northeastern University (December 2011)}
\cvlistitem{Harvard University (December 2011)}
\cvlistitem{Google - New York (July 2011)}
\cvlistitem{New York University (April 2011)}

\subsection{Invited Panels}
\cvline{2016}{``What I wish I knew when I started grad school,'' Programming Languages Mentoring Workshop (PLMW) at the Progrmamming Languages Design and Implementation (PLDI) conference, Santa Barbara, CA, 2016.}{}

\subsection{Selected Public Speaking}
\cvline{2017}{``Programming Languages for Biological Modeling,'' WECode Harvard, Cambridge, MA (February 2017).}
\cvline{2016}{``Meet the Innovators Under 35,'' \emph{MIT Technology Review} EmTech Conference, Cambridge, MA (September 2016).}{}
\cvline{}{``Securing Software by Construction,'' Philly Emerging Tech Conference, Philadelphia, PA (April 2016).}{}
\cvline{2015}{``On the Front Lines: New Risks and Knowledge,'' panel at \emph{AtlanticLIVE}'s ``Cybersecurity Today'' summit, Washington, DC (October 2015).}{}
\cvline{}{``Cybersecurity: How to Use What We Already Know,'' keynote at PrivacySecurityRisk, Las Vegas, NV (October 2015).}{}
\cvline{2014}{`A Brief History of Programming''}{}
\cvlistitem{Geek Girl Dinner Boston, Cambridge, MA (December 2014).}
\cvlistitem{Women's Coding Collective Boston, Cambridge, MA (December 2014).}
\cvline{}{``An Axiomatic Basis for Computer Programming,'' Papers We Love NYC, New York, NY (November 2014).}{}
\cvline{}{``Challenging Technical Privilege: How Race and Gender Matter,'' MIT, Cambridge, MA (October 2014).}{}
\cvline{2013}{``Graduate School 101,'' panel at Scientista Symposium, MIT, Cambridge, MA (April 2013).}{}
\cvline{}{``How I Got There,'' panel at Women in Advanced Computing (WiAC) Summit, San Jose, CA (June 2013).}{}

\subsection{Selected Podcast Appearances}
\cvline{2017}{``Secure Programming with Jean Yang,'' \emph{The Women in Tech Show}, February 13, 2017.}{}
\cvline{2015}{``Three Female Computer Scientists Walk into an AMA,'' \emph{Upvoted}, February 18, 2015.}{}
