\section{Teaching}
\cventry{Spring 2017}{Co-Instructor, Software Foundations of Security and Privacy (15-316)}{Carnegie Mellon University}{}
  {}{Co-designed and co-taught new undergraduate course with Matthew Fredrikson, with goal of teaching students to formally specify and prove security and privacy properties, with topics including safety, information flow, and statistical privacy. Reviews averaged 4.7/5.0 (teaching) and 4.6/5.0 (course) with course size 12.}
  \cvlistitem{``Awesome class, good presentation and interesting topics.''}
  \cvlistitem{``\dots I made \$1000 from this course! After learning about implicit flows, I was able to identify security bugs in Instagram, caused by their lack of information flow control. Since it was a security bug, I received a reward from their bug bounty program.''}
  \cvlistitem{``\dots I really liked this class! It was great to look at these security concepts in a functional programming context.''}
  \cvlistitem{``Jean also gave some really great lectures, especially the more technical ones about information flow type systems.''}
  \cvlistitem{``I liked the course very much and the homework load was very fair.''}
  \cvlistitem{``Lectures were really fun and \emph{[sic]} felt like I learned a lot over the course of the semester.''}
\cventry{Fall 2016}{Instructor, Domain-Specific Languages (15-819)}{Carnegie Mellon University}{}
  {}{Designed and taught experimental discussion-based graduate special topics seminar on programming language design and evaluation across a variety of domains, with focused units on systems programming, security and privacy, and biological modelling. Reviews averaged 4.6/5.0 (teaching) and 4.0/5.0 (course) with course size of 8.}
\cvlistitem{"Definitely offer this course again and at the undergraduate level. Not many discussion-based courses happen in CS and they should."}
\cvlistitem{"I feel like this course gave me a great opportunity to read a bunch of DSL papers and really understand the current state of the field. Thanks for a great semester!"}
\cventry{Fall 2010}{Teaching Assistant, Foundations of Program Analysis}{Massachusetts Institute of Technology}{}
  {}{Designed and graded assignments and held recitations for graduate-level program analysis course.}
\cventry{January 2010}{Instructor, C Memory Management and C++ Object-Oriented Programming}{Massachusetts Institute of Technology}{}
  {}{Designed and co-taught a for-credit Independent Activities Period (IAP) course for over 100 undergraduates.  Prepared lectures and assignments; managed multiple graders; published materials on MIT's Open Courseware.}
\cventry{January 2010}{Instructor, So You've Always Wanted to Learn Haskell?}{Massachusetts Institute of Technology}{}
  {}{Designed and co-taught an Independent Activities Period (IAP) course introducing the Haskell language and its applications.}
\cventry{Spring 2008}{Teaching Fellow, Principles of Programming Languages}{Harvard University}{}
  {}{Helped with new course introducing programming languages concepts using the Coq proof assistant.  Effectiveness rating 4.6/5.0.  Received Certificate of Distinction in Teaching.}
\cventry{Spring 2007}{Teaching Fellow, Introduction to Computer Science II}{Harvard University}{}{}
  {Responsible for problem sets, exams, section, and office hours for course using Scheme and C++.  Effectiveness rating 4.6/5.0; nominated for Undergraduate Council's Levenson Teaching Prize.}
\cventry{Fall 2006}{Teaching Fellow, Introduction to Formal Systems}{Harvard University}{}{}
  {Responsible for problem sets, exams, section, and office hours for course on computational models and complexity.  Effectiveness rating 4.2/5.0.  Nominated for departmental teaching award.}
\cventry{Fall 2005}{Course Assistant, Introduction to Calculus}{Harvard University}{}{}
  {Graded problem sets and ran weekly problem session.  Effectiveness rating rating 4.4/5.0.}
