\section{Writing for the Public}

\subsection{Articles About Technology}
\cvline{2017}{``James Comey's Twitter Security Problem Is Your Problem, Too,'' \textbf{Jean Yang}, \emph{MIT Technology Review}, April 27, 2017.}{}
\cvline{}{``Building privacy right into software code,'' \textbf{Jean Yang}, \emph{The Conversation}, February 20, 2017.}{}
\cvline{2016}{``Research for Practice: Web Security and Mobile Web Computing,'' \textbf{Jean Yang}, \emph{ACM Queue}, October 4, 2016.}{}
\cvline{}{``The robot apocalypse is here: and it's not what we expected,'' \textbf{Jean Yang}, \emph{ACM SIGCAS}, March 2016.}{}
\cvline{}{``Making It Easy to Make Apps.'' \textbf{Jean Yang}, \emph{MIT Technology Review}, June 21, 2016.}{}
\cvline{2015}{``The Real Software Security Problem is Us.'' \textbf{Jean Yang}, \emph{MIT Technology Review}, June 22, 2015.}{}
\cvline{}{``C is Manly, Python is for 'n00bs': How False Stereotypes Turn Into Technical 'Truths.''' \textbf{Jean Yang} and Ariel Rabkin, \emph{Model View Culture}, January 20, 2015.}{}

\subsection{Other Articles}
\cvline{2016}{``Sex, Crime, and Justice,'' \textbf{Jean Yang}, \emph{Jacobin Magazine}, September 30, 2016.}{}
\cvline{2014}{``MIT Computer Scientists Demonstrate the Hard Way that Gender Still Matters,'' Elena Glassman, Neha Narula, and \textbf{Jean Yang}, \emph{Wired}, December 29, 2014.}{}
\cvline{}{``I Worked Without Email for 10 Days, Survived, and Even Learned Something,'' \textbf{Jean Yang}, \emph{Newsweek} via \emph{The Daily Muse}, September 16, 2014.}{}
\cvline{}{``First person / The power of girls,'' \textbf{Jean Yang}, \emph{Pittsburgh Post-Gazette}, May 31, 2014.}{}
\cvline{}{``Only Woman on the Team? 4 Communication Tips You Need to Know,'' \textbf{Jean Yang}, \emph{Forbes} via \emph{The Daily Muse}, March 26, 2014.}{}

\subsection{Popular Blog Posts}
\cvline{2016}{``What to Wear for Academic Interviews, or How to Dress Like a Man Without Looking Like a Man,'' \emph{Blogger}, December 25, 2015.}{}
\cvline{}{``Why It's Not Academia's Job to Produce Code That Ships,'' \emph{Blogger}, May 7, 2016.}{}
\cvline{}{``What My PhD Was Like,'' \emph{Blogger}, February 27, 2016.}{}
\cvline{2015}{``What do you think of Scott Aaronson's comment \#171 and the subsequent posts?,'' \emph{Quora}, January 12, 2015.}{}
\cvline{2014}{``Speaking Fake-Polish is No Different from Speaking `Male,''' \emph{Medium}, February 4, 2014.}{}
